---
title: "Case Study: Cyclistic"
author: "Junior Sundar"
date: 22-August-2023
format: html
editor: 
  - render-on-save: true
---

```{r load libraries, include=FALSE}
# install.packages("tidyverse", repos = "https://cran.nyuad.nyu.edu/")
# install.packages("ggplot2", repos = "https://cran.nyuad.nyu.edu/")
# install.packages("formattable", repos = "https://cran.nyuad.nyu.edu/")
library(tidyverse)
library(ggplot2)
library(formattable)
```


# **Scenario**

To access original document, click [here](https://d3c33hcgiwev3.cloudfront.net/aacF81H_TsWnBfNR_x7FIg_36299b28fa0c4a5aba836111daad12f1_DAC8-Case-Study-1.pdf?Expires=1692835200&Signature=FiC7NLNZqLvn8VgO~z-7Mzkyph2~NOoX4bof~hX0TI~iuL~qkHjWcNFxPtdGQdccv6g5XuMVAQST~pQ3JlOJwwpqZg-xR0zqyXEcg~ndqhOHC4W40G~tqZ95~CCJEBJdFEjrts-Qn8BKvikChbO7RATc7WGRCBuvvKG3G1P47pA_&Key-Pair-Id=APKAJLTNE6QMUY6HBC5A)!

The director of marketing of Cyclistic (finctional bike-share company in Chicago) believes the company’s future success depends on maximizing the number of annual memberships. Therefore, the team wants to understand how casual riders and annual members use Cyclistic bikes differently. From these insights, the team will design a new marketing strategy to convert casual riders into annual members.

Until now, Cyclistic’s marketing strategy relied on building general awareness and appealing to broad consumer segments. One approach that helped make these things possible was the flexibility of its pricing plans: single-ride passes, full-day passes, and annual memberships. Customers who purchase single-ride or full-day passes are referred to as casual riders. Customers who purchase annual memberships are Cyclistic members. Cyclistic’s finance analysts have concluded that annual members are much more profitable than casual riders. 

# **STEP 1**: Ask

## Defining the Problem

Design marketing strategies aimed at converting casual riders into annual members. In order todo that, however, the marketing analyst team needs to answer the following questions:

1. How do annual members and casual riders use Cyclistic bikes differently?
2. Why would casual riders by Cyclistic annual memberships?
3. How can Cyclistic use digital media to influence casual riders to become members?

This Case Study will attempt to answer the first question: "How do annual members and casual riders use Cyclistic bikes differently?"

The answer to this question will provide the marketing team with the proper insight needed to tailor the underlying message and purpose of their marketing strategies to target the target audience: casual riders.

## Business Task

Analyse historical bike trip data to identify trends in how annual members and casual riders use Cyclistic bikes differently.

## Key Stakeholders

* __Director of Marketing (Manager)__: Responsible for development of campaigns and initiatives to promote the bike-share program.

* __Cyclistic Marketing Analytics Team__: Team of data analysts whoa re responsible for collectiong, analysing and reporting data to help guide Cyclistic marketing strategy.

* __Cyclistic Executive Team__: Executive team that will decide upon and approve recommended marketing program.

# **STEP 2**: Prepare

## Data Source

Historical bike trip data for previous 12 months are used to identify and analyse trends. Since Cyclistic is a fictional company, an alternate (publicly available) data source is used. The data is made available by Motivate International Inc. available [here](https://divvy-tripdata.s3.amazonaws.com/index.html).

The raw data is downloaded and made available in `.csv` format in the folder `./dataset_12_months`.

## Data Structure

The data is organised in rows and colums.

```{r sample data, warning=FALSE, echo=FALSE}
sample_data <- read.csv('./dataset_12_months/202208-divvy-tripdata.csv')
column_names <- colnames(sample_data)

descriptions <- c("ID",
                  "Bike Type",
                  "Trip start date-time",
                  "Trip end date-time",
                  "Trip start station",
                  "Trip start station ID",
                  "Trip end station",
                  "Trip end station ID",
                  "Trip start latitude",
                  "Trip start longitude",
                  "Trip end latitude",
                  "Trip end longitude",
                  "Rider type - member or casual"
                  )

summary_frame = data.frame(column_names, descriptions)
formattable(summary_frame,
            align = c("l", "l"))

```